---
title: "Wells Fargo Competition"
subtitle: "Identify which outreach methods & channels yield the best product portfolio"
author: "Shishir Shirbhate"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  pdf_document: 
    toc: yes
---

\newpage
# 1. Load Libraries

```{r, message=FALSE, warning=FALSE,results='hide'}
suppressPackageStartupMessages({
library(data.table)
library(ggplot2)
library(dplyr)
library(Hmisc)
library(rpart)
library(caret)
library(e1071)
library(pscl)
library(reshape)
library(plm)
library(gplots)
library(fields)
library(arules)
library(arulesViz)
library(gridExtra)
library(MASS)
library(reshape2)
library(coefplot)
})
```

# 2. Data Insertion & summarization

```{r}

file_path <- "C:/MS Material/Competitions/Wells Fargo/Campus Challenge.csv"

bank_data = read.table(file=file_path, header=TRUE, sep = ",")

head(bank_data)
summary(bank_data)
describe(bank_data)

```

# 3. Data Wrangling & Feature Engineering

```{r}

bank_data$portfolio <- bank_data$typeA_ct + bank_data$typeB_ct + 
  bank_data$typeC_flag + bank_data$typeD_flag + bank_data$typeE_flag + bank_data$typeF_flag + bank_data$typeG_flag

# Find change in balance from previous month
setDT(bank_data)[,balance_change:=bank_data$normal_tot_bal-shift(bank_data$normal_tot_bal,1,type="lag")]

bank_data$balance_change[which(bank_data$month == 1)] <- 0

# Find change in portfolio from previous month
setDT(bank_data)[,portfolio_change:=bank_data$portfolio-shift(bank_data$portfolio,1,type="lag")]

bank_data$portfolio_change[which(bank_data$month == 1)] <- 0

# Flag increase / decrease in balance
bank_data$balance_change_flag <- NA
bank_data$balance_change_flag[which(bank_data$balance_change < 0)] <- 0
bank_data$balance_change_flag[which(bank_data$balance_change > 0)] <- 1
bank_data$balance_change_flag[which(bank_data$balance_change == 0)] <- 0

# Flag increase / decrease in portfolio
bank_data$portfolio_change_flag <- NA
bank_data$portfolio_change_flag[which(bank_data$portfolio_change < 0)] <- 0
bank_data$portfolio_change_flag[which(bank_data$portfolio_change > 0)] <- 1
bank_data$portfolio_change_flag[which(bank_data$portfolio_change == 0)] <- 0

# Customer Outreaches changes and flags

setDT(bank_data)[,cust_outreach_ai_change:=bank_data$cust_outreach_ai -
                   shift(bank_data$cust_outreach_ai,1,type="lag")]
bank_data$cust_outreach_ai_change[which(bank_data$month == 1)] <- 0
bank_data$cust_outreach_ai_flag <- NA
bank_data$cust_outreach_ai_flag[which(bank_data$cust_outreach_ai_change < 0)] <- 0
bank_data$cust_outreach_ai_flag[which(bank_data$cust_outreach_ai_change > 0)] <- 1
bank_data$cust_outreach_ai_flag[which(bank_data$cust_outreach_ai_change == 0)] <- 0

setDT(bank_data)[,cust_outreach_aii_change:=bank_data$cust_outreach_aii -
                   shift(bank_data$cust_outreach_aii,1,type="lag")]
bank_data$cust_outreach_aii_change[which(bank_data$month == 1)] <- 0
bank_data$cust_outreach_aii_flag <- NA
bank_data$cust_outreach_aii_flag[which(bank_data$cust_outreach_aii_change < 0)] <- 0
bank_data$cust_outreach_aii_flag[which(bank_data$cust_outreach_aii_change > 0)] <- 1
bank_data$cust_outreach_aii_flag[which(bank_data$cust_outreach_aii_change == 0)] <- 0

setDT(bank_data)[,cust_outreach_aiii_change:=bank_data$cust_outreach_aiii -
                   shift(bank_data$cust_outreach_aiii,1,type="lag")]
bank_data$cust_outreach_aiii_change[which(bank_data$month == 1)] <- 0
bank_data$cust_outreach_aiii_flag <- NA
bank_data$cust_outreach_aiii_flag[which(bank_data$cust_outreach_aiii_change < 0)] <- 0
bank_data$cust_outreach_aiii_flag[which(bank_data$cust_outreach_aiii_change > 0)] <- 1
bank_data$cust_outreach_aiii_flag[which(bank_data$cust_outreach_aiii_change == 0)] <- 0

setDT(bank_data)[,cust_outreach_aiv_change:=bank_data$cust_outreach_aiv -
                   shift(bank_data$cust_outreach_aiv,1,type="lag")]
bank_data$cust_outreach_aiv_change[which(bank_data$month == 1)] <- 0
bank_data$cust_outreach_aiv_flag <- NA
bank_data$cust_outreach_aiv_flag[which(bank_data$cust_outreach_aiv_change < 0)] <- 0
bank_data$cust_outreach_aiv_flag[which(bank_data$cust_outreach_aiv_change > 0)] <- 1
bank_data$cust_outreach_aiv_flag[which(bank_data$cust_outreach_aiv_change == 0)] <- 0

setDT(bank_data)[,cust_outreach_av_change:=bank_data$cust_outreach_av -
                   shift(bank_data$cust_outreach_av,1,type="lag")]
bank_data$cust_outreach_av_change[which(bank_data$month == 1)] <- 0
bank_data$cust_outreach_av_flag <- NA
bank_data$cust_outreach_av_flag[which(bank_data$cust_outreach_av_change < 0)] <- 0
bank_data$cust_outreach_av_flag[which(bank_data$cust_outreach_av_change > 0)] <- 1
bank_data$cust_outreach_av_flag[which(bank_data$cust_outreach_av_change == 0)] <- 0

setDT(bank_data)[,cust_outreach_avi_change:=bank_data$cust_outreach_avi -
                   shift(bank_data$cust_outreach_avi,1,type="lag")]
bank_data$cust_outreach_avi_change[which(bank_data$month == 1)] <- 0
bank_data$cust_outreach_avi_flag <- NA
bank_data$cust_outreach_avi_flag[which(bank_data$cust_outreach_avi_change < 0)] <- 0
bank_data$cust_outreach_avi_flag[which(bank_data$cust_outreach_avi_change > 0)] <- 1
bank_data$cust_outreach_avi_flag[which(bank_data$cust_outreach_avi_change == 0)] <- 0

setDT(bank_data)[,cust_outreach_avii_change:=bank_data$cust_outreach_avii -
                   shift(bank_data$cust_outreach_avii,1,type="lag")]
bank_data$cust_outreach_avii_change[which(bank_data$month == 1)] <- 0
bank_data$cust_outreach_avii_flag <- NA
bank_data$cust_outreach_avii_flag[which(bank_data$cust_outreach_avii_change < 0)] <- 0
bank_data$cust_outreach_avii_flag[which(bank_data$cust_outreach_avii_change > 0)] <- 1
bank_data$cust_outreach_avii_flag[which(bank_data$cust_outreach_avii_change == 0)] <- 0

setDT(bank_data)[,cust_outreach_aviii_change:=bank_data$cust_outreach_aviii -
                   shift(bank_data$cust_outreach_aviii,1,type="lag")]
bank_data$cust_outreach_aviii_change[which(bank_data$month == 1)] <- 0
bank_data$cust_outreach_aviii_flag <- NA
bank_data$cust_outreach_aviii_flag[which(bank_data$cust_outreach_aviii_change < 0)] <- 0
bank_data$cust_outreach_aviii_flag[which(bank_data$cust_outreach_aviii_change > 0)] <- 1
bank_data$cust_outreach_aviii_flag[which(bank_data$cust_outreach_aviii_change == 0)] <- 0

bank_data$binary_channels <- paste(bank_data$wf_outreach_flag_chan_i,
                                   bank_data$wf_outreach_flag_chan_ii,
                                   bank_data$wf_outreach_flag_chan_iv,sep="")
bank_data$demo_combo <- paste(bank_data$cust_demographics_ai,bank_data$cust_demographics_aii,sep="")


bank_data$channel_combination <- strtoi(bank_data$binary_channels,base=2)

```

# 3. Change data types

```{r}

bank_data$cust_demographics_ai <- as.factor(bank_data$cust_demographics_ai)
bank_data$cust_demographics_aii <- as.factor(bank_data$cust_demographics_aii)

bank_data$channel_combinationF <- as.factor(bank_data$channel_combination)

bank_data$monthF <- as.factor(bank_data$month)

bank_data$typeA_bal_cat <- as.factor(bank_data$typeA_bal_cat)
bank_data$typeB_bal_cat <- as.factor(bank_data$typeB_bal_cat)
bank_data$typeC_bal_cat <- as.factor(bank_data$typeC_bal_cat)
bank_data$typeD_bal_cat <- as.factor(bank_data$typeD_bal_cat)
bank_data$typeE_bal_cat <- as.factor(bank_data$typeE_bal_cat)

```

# 4. Data Exploration

```{r}

ggplot(bank_data, aes(x=portfolio)) + 
  geom_bar(color="blue",fill="blue") + 
  xlab("Portfolio")+  
  scale_x_continuous(breaks = seq(0,max(bank_data$portfolio),1)) +
  theme(axis.title.x = element_text(face="bold", size=16),axis.text.x  = element_text(angle=0, vjust=0.5, size=16)) + 
  theme(axis.title.y = element_text(face="bold", size=16),axis.text.y  = element_text(angle=0, vjust=0.5, size=16))

# Check if first bar can be made of different color
portfolio_channel <- ggplot(bank_data, aes(x=channel_combination,y=portfolio_change_flag)) + 
  geom_bar(stat="identity",color="blue",fill="blue") + 
  stat_summary(fun.y="mean", geom="bar") + 
  xlab("Channel Combinations") +
  ylab("Avg no. of Portfolio Increases") + 
  scale_x_continuous(breaks = seq(0,7,1)) + 
  theme(axis.title.x = element_text(face="bold", size=16),axis.text.x  = element_text(angle=0, vjust=0.5, size=16)) + 
  theme(axis.title.y = element_text(face="bold", size=16),axis.text.y  = element_text(angle=0, vjust=0.5, size=16))

balance_channel <- ggplot(bank_data, aes(x=channel_combination,y=balance_change_flag)) + 
  geom_bar(stat="identity",color="blue",fill="white") + 
  stat_summary(fun.y="mean", geom="bar") + 
  xlab("Channel Combinations") +
  ylab("Avg no. of times Balance Increases") + 
  scale_x_continuous(breaks = seq(0,7,1)) + 
  theme(axis.title.x = element_text(face="bold", size=16),axis.text.x  = element_text(angle=0, vjust=0.5, size=16)) + 
  theme(axis.title.y = element_text(face="bold", size=16),axis.text.y  = element_text(angle=0, vjust=0.5, size=16))

portfolio_demo_A <- ggplot(bank_data, aes(x=cust_demographics_ai,y=portfolio_change_flag)) + 
  geom_bar(stat="identity",color="blue",fill="blue") + 
  stat_summary(fun.y="mean", geom="bar") +
  xlab("Demographics Type A") +
  ylab("Avg no. of Portfolio Increases") + 
  theme(axis.title.x = element_text(face="bold", size=16),axis.text.x  = element_text(angle=0, vjust=0.5, size=16)) + 
  theme(axis.title.y = element_text(face="bold", size=16),axis.text.y  = element_text(angle=0, vjust=0.5, size=16))

balance_demo_A <- ggplot(bank_data, aes(x=cust_demographics_ai,y=balance_change_flag)) + 
  geom_bar(stat="identity",color="blue",fill="white") + 
  stat_summary(fun.y="mean", geom="bar") + 
  xlab("Demographics Type A") +
  ylab("Avg no. of times Balance Increases") + 
  theme(axis.title.x = element_text(face="bold", size=16),axis.text.x  = element_text(angle=0, vjust=0.5, size=16)) + 
  theme(axis.title.y = element_text(face="bold", size=16),axis.text.y  = element_text(angle=0, vjust=0.5, size=16))

portfolio_demo_B <- ggplot(bank_data, aes(x=cust_demographics_aii,y=portfolio_change_flag)) + 
  geom_bar(stat="identity",color="blue",fill="blue") + 
  stat_summary(fun.y="mean", geom="bar") + 
  xlab("Demographics Type B") +
  ylab("Avg no. of Portfolio Increases") + 
  theme(axis.title.x = element_text(face="bold", size=16),axis.text.x  = element_text(angle=0, vjust=0.5, size=16)) + 
  theme(axis.title.y = element_text(face="bold", size=16),axis.text.y  = element_text(angle=0, vjust=0.5, size=16))

balance_demo_B <- ggplot(bank_data, aes(x=cust_demographics_aii,y=balance_change_flag)) + 
  geom_bar(stat="identity",color="blue",fill="white") + 
  stat_summary(fun.y="mean", geom="bar") + 
  xlab("Demographics Type B") + 
  ylab("Avg no. of times Balance Increases") + 
  theme(axis.title.x = element_text(face="bold", size=16),axis.text.x  = element_text(angle=0, vjust=0.5, size=16)) + 
  theme(axis.title.y = element_text(face="bold", size=16),axis.text.y  = element_text(angle=0, vjust=0.5, size=16))

#multiple graphs on one panel
grid.arrange(portfolio_channel,portfolio_demo_A,portfolio_demo_B,balance_channel,balance_demo_A,balance_demo_B, ncol=3)

```

# 5. Check Association between portfolio change and customer outreaches change

```{r}

association_data <- subset(bank_data,select=c("portfolio_change_flag",
                                "cust_outreach_ai_flag",
                                "cust_outreach_aii_flag",
                                "cust_outreach_aiii_flag",
                                "cust_outreach_aiv_flag",
                                "cust_outreach_av_flag",
                                "cust_outreach_avi_flag",
                                "cust_outreach_avii_flag",
                                "cust_outreach_aviii_flag",
                                "wf_outreach_flag_chan_i",
                                "wf_outreach_flag_chan_ii",
                                "wf_outreach_flag_chan_iv"))

transaction <- as(data.matrix(association_data), "transactions")

itemFrequencyPlot(transaction,topN=20,type="absolute")

rules <- apriori(data = transaction, parameter = list(support = 0.001, confidence = 0.005))

rules <- sort(rules,by="confidence",decreasing=TRUE)

#inspect(rules[1:3])

rules_subset <- subset(rules, subset = rhs %pin% "portfolio_change_flag" & lift > 0)[1:3]
  
inspect(rules_subset)

plot(rules_subset)

# Confidence - This is the primary mode of sorting since we want to know out of all balance increases
# which combinations of outreaches & channels occur the most frequently

# Support - We have put a cut-off of 10% of actual proportion of portfolio changes

# Lift - Combinations of <> outreaches and channels are <>% more likely to have balance increases

```

# 6. Check Association between balance change and customer outreaches change

```{r}

association_data <- subset(bank_data,select=c("balance_change_flag",
                                              "cust_outreach_ai_flag",
                                              "cust_outreach_aii_flag",
                                              "cust_outreach_aiii_flag",
                                              "cust_outreach_aiv_flag",
                                              "cust_outreach_av_flag",
                                              "cust_outreach_avi_flag",
                                              "cust_outreach_avii_flag",
                                              "cust_outreach_aviii_flag",
                                              "wf_outreach_flag_chan_i",
                                              "wf_outreach_flag_chan_ii",
                                              "wf_outreach_flag_chan_iv"))

transaction <- as(data.matrix(association_data), "transactions")

itemFrequencyPlot(transaction,topN=20,type="absolute")

rules <- apriori(data = transaction, parameter = list(support = 0.05, confidence = 0.005))

rules <- sort(rules,by="confidence",decreasing=TRUE)

rules_subset <- subset(rules, subset = rhs %pin% "balance_change_flag" & lift > 0)[1:3]

inspect(rules_subset)

plot(rules_subset)
plot(rules_subset,method="graph")
plot(rules_subset,method="grouped")

# Confidence - This is the primary mode of sorting since we want to know out of all balance increases
# which combinations of outreaches & channels occur most frequently

# Support - We have put a cut-off of 10% of actual proportion of balance changes

# Lift - Combinations of <> outreaches and channels are <>% more likely to have balance increases

```

# 7. Finding correlations of various outreach programs with portfolio

```{r}

demo1_portfolio <- data.frame(matrix(nrow=8,ncol=6))
colnames(demo1_portfolio) <- c("0","1","2","3","4","5")

for (i in 1:length(unique(bank_data$cust_demographics_ai)))
{
  bank_data1 <- bank_data[bank_data$cust_demographics_ai == i-1]
  for (j in 1:nrow(demo1_portfolio))
  {
    if (j == 1)
    {
      demo1_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_ai),2)
    }else if(j==2)
    {
      demo1_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_aii),2)
    }else if(j==3)
    {
      demo1_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_aiii),2)
    }else if(j==4)
    {
      demo1_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_aiv),2)
    }else if(j==5)
    {
      demo1_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_av),2)
    }else if(j==6)
    {
      demo1_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_avi),2)
    }else if(j==7)
    {
      demo1_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_avii),2)
    }else
    {
      demo1_portfolio[[i]][j]<- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_aviii),2)
    }
  }
}

demo2_portfolio <- data.frame(matrix(nrow=8,ncol=5))
colnames(demo2_portfolio) <- c("1","2","3","4","5")

for (i in 1:length(unique(bank_data$cust_demographics_aii)))
{
  bank_data1 <- bank_data[bank_data$cust_demographics_aii == i]
  for (j in 1:nrow(demo2_portfolio))
  {
    if (j == 1)
    {
      demo2_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_ai),2)
    }else if(j==2)
    {
      demo2_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_aii),2)
    }else if(j==3)
    {
      demo2_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_aiii),2)
    }else if(j==4)
    {
      demo2_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_aiv),2)
    }else if(j==5)
    {
      demo2_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_av),2)
    }else if(j==6)
    {
      demo2_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_avi),2)
    }else if(j==7)
    {
      demo2_portfolio[[i]][j] <- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_avii),2)
    }else
    {
      demo2_portfolio[[i]][j]<- round(cor(bank_data1$portfolio,bank_data1$cust_outreach_aviii),2)
    }
  }
}

demo1_bal <- data.frame(matrix(nrow=8,ncol=6))
colnames(demo1_bal) <- c("0","1","2","3","4","5")

for (i in 1:length(unique(bank_data$cust_demographics_ai)))
{
  bank_data1 <- bank_data[bank_data$cust_demographics_ai == i-1]
  for (j in 1:nrow(demo1_bal))
  {
    if (j == 1)
    {
      demo1_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_ai),2)
    }else if(j==2)
    {
      demo1_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_aii),2)
    }else if(j==3)
    {
      demo1_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_aiii),2)
    }else if(j==4)
    {
      demo1_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_aiv),2)
    }else if(j==5)
    {
      demo1_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_av),2)
    }else if(j==6)
    {
      demo1_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_avi),2)
    }else if(j==7)
    {
      demo1_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_avii),2)
    }else
    {
      demo1_bal[[i]][j]<- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_aviii),2)
    }
  }
}

demo2_bal <- data.frame(matrix(nrow=8,ncol=5))
colnames(demo2_bal) <- c("1","2","3","4","5")

for (i in 1:length(unique(bank_data$cust_demographics_aii)))
{
  bank_data1 <- bank_data[bank_data$cust_demographics_aii == i]
  for (j in 1:nrow(demo2_bal))
  {
    if (j == 1)
    {
      demo2_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_ai),2)
    }else if(j==2)
    {
      demo2_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_aii),2)
    }else if(j==3)
    {
      demo2_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_aiii),2)
    }else if(j==4)
    {
      demo2_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_aiv),2)
    }else if(j==5)
    {
      demo2_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_av),2)
    }else if(j==6)
    {
      demo2_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_avi),2)
    }else if(j==7)
    {
      demo2_bal[[i]][j] <- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_avii),2)
    }else
    {
      demo2_bal[[i]][j]<- round(cor(bank_data1$normal_tot_bal,bank_data1$cust_outreach_aviii),2)
    }
  }
}

# Demographics A - Portfolio
image(as.matrix(demo1_portfolio),axes=F)
mtext(text=c(1:nrow(demo1_portfolio)), side=1, line=0.3, at=seq(0,1,1/(nrow(demo1_portfolio)-1)), las=1, cex=0.8)
mtext(text=c(0:(ncol(demo1_portfolio)-1)), side=2, line=0.3, at=seq(0,1,1/(ncol(demo1_portfolio)-1)), las=1, cex=0.8)
for (x in 1:nrow(demo1_portfolio))
  for (y in 1:ncol(demo1_portfolio))
    text((x-1)/(nrow(demo1_portfolio)-1), (y-1)/(ncol(demo1_portfolio)-1), 
         sprintf("%0.2f", demo1_portfolio[x,y]))

# Demographics A - Balance
image(as.matrix(demo1_bal),axes=F)
mtext(text=c(1:nrow(demo1_bal)), side=1, line=0.3, at=seq(0,1,1/(nrow(demo1_bal)-1)), las=1, cex=0.8)
mtext(text=c(0:(ncol(demo1_bal)-1)), side=2, line=0.3, at=seq(0,1,1/(ncol(demo1_bal)-1)), las=1, cex=0.8)
for (x in 1:nrow(demo1_bal))
  for (y in 1:ncol(demo1_bal))
    text((x-1)/(nrow(demo1_bal)-1), (y-1)/(ncol(demo1_bal)-1), 
         sprintf("%0.2f", demo1_bal[x,y]))

# Demographics B - Portfolio
image(as.matrix(demo2_portfolio),axes=F)
mtext(text=c(1:nrow(demo2_portfolio)), side=1, line=0.3, at=seq(0,1,1/(nrow(demo2_portfolio)-1)), las=1, cex=0.8)
mtext(text=c(1:ncol(demo2_portfolio)), side=2, line=0.3, at=seq(0,1,1/(ncol(demo2_portfolio)-1)), las=1, cex=0.8)
for (x in 1:nrow(demo2_portfolio))
  for (y in 1:ncol(demo2_portfolio))
    text((x-1)/(nrow(demo2_portfolio)-1), (y-1)/(ncol(demo2_portfolio)-1), 
         sprintf("%0.2f", demo2_portfolio[x,y]))


# Demographics B - Balance
image(as.matrix(demo2_bal),axes=F)
mtext(text=c(1:nrow(demo2_bal)), side=1, line=0.3, at=seq(0,1,1/(nrow(demo2_bal)-1)), las=1, cex=0.8)
mtext(text=c(1:ncol(demo2_bal)), side=2, line=0.3, at=seq(0,1,1/(ncol(demo2_bal)-1)), las=1, cex=0.8)
for (x in 1:nrow(demo2_bal))
  for (y in 1:ncol(demo2_bal))
    text((x-1)/(nrow(demo2_bal)-1), (y-1)/(ncol(demo2_bal)-1), 
         sprintf("%0.2f", demo2_bal[x,y]))

# image.plot(as.matrix(demo2_bal),axes=F)

```

# 8. Modeling

```{r}

#Create model to predict change in total balance -- find which methods increase balance!
balance_model<-lm(balance_change~month+cust_outreach_ai+
                    cust_outreach_aiii, data=bank_data)

#Create model to predict change in portfolio
portfolio_model<-lm(portfolio_change~ month + cust_demographics_ai + 
                      cust_demographics_aii + typeA_ct + typeB_ct + typeA_bal_cat + 
                      typeC_bal_cat + typeE_bal_cat + 
                      typeF_flag + cust_outreach_ai + cust_outreach_aii + 
                      cust_outreach_aiii + cust_outreach_aiv + 
                      cust_outreach_avi + cust_outreach_avii + 
                      wf_outreach_flag_chan_i + wf_outreach_flag_chan_ii, 
                    data = bank_data)


##What drives growth in account balance?

bal_growth_model<-glm(balance_change_flag ~ cust_outreach_ai+cust_outreach_aiii+cust_outreach_aiv+
                        cust_outreach_avi+cust_outreach_avii+cust_outreach_aviii
                      +channel_combination, data=bank_data, 
                      family="binomial")

sort(exp(coef(bal_growth_model)), decreasing = TRUE)


#growth in number of accounts?

portfolio_model<-glm(portfolio_change_flag~cust_outreach_ai+cust_outreach_aii+ 
                       cust_outreach_aiii+cust_outreach_aiv+cust_outreach_av+
                       cust_outreach_avi+cust_outreach_avii
                     +channel_combination+cust_demographics_ai, data=bank_data, 
                     family="binomial")

sort(exp(coef(portfolio_model)), decreasing = TRUE)


## demographic regressions

bank_data$balance_change_flag_new <- NA
bank_data$balance_change_flag_new[which(bank_data$balance_change < 0)] <- -1
bank_data$balance_change_flag_new[which(bank_data$balance_change > 0)] <- 1
bank_data$balance_change_flag_new[which(bank_data$balance_change == 0)] <- 0

bank_data$portfolio_change_flag_new <- NA
bank_data$portfolio_change_flag_new[which(bank_data$portfolio_change < 0)] <- -1
bank_data$portfolio_change_flag_new[which(bank_data$portfolio_change > 0)] <- 1
bank_data$portfolio_change_flag_new[which(bank_data$portfolio_change == 0)] <- 0

bank_data$balance_change_flag_new<-as.factor(bank_data$balance_change_flag_new)
bank_data$portfolio_change_flag_new<-as.factor(bank_data$balance_change_flag_new)


bank_data$month<-as.integer(bank_data$month)

portfolio_order_model<-polr(portfolio_change_flag_new~cust_demographics_ai+cust_demographics_aii+month, data=bank_data, Hess=TRUE)
ctable<-coef(summary(portfolio_order_model))

p<-pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable<-cbind(ctable, "p value" = p)
sort(exp(coef(portfolio_order_model)), decreasing = TRUE)

newdat<-data.frame(cust_demographics_ai = as.factor(rep(0:5, 200)),
  cust_demographics_aii = as.factor(rep(1:5, 240)),
  month = rep(1:12, each = 100))

prediction<- cbind(newdat, predict(portfolio_order_model, newdat, type = "probs"))

lnewdat<-melt(prediction, id.vars = c("cust_demographics_ai", "cust_demographics_aii", "month"),
              variable.name = "Level", value.name = "Probability")

colnames(lnewdat) <- c("cust_demographics_ai","cust_demographics_aii","month","Level","Probability")

labels<-lnewdat

labels$Demo1<-labels$cust_demographics_ai
labels$Demo2<-labels$cust_demographics_aii

ggplot(subset(labels,Demo1 %in% c("2","3","4")& Demo2 %in% c("3","4","5")), aes(x=month, y=Probability, color = Level))+ 
  geom_line() + facet_grid(Demo1~Demo2, labeller = "label_both")+ 
  ggtitle("Demographic Matrix") + scale_x_continuous(breaks=seq(1, 12, 1)) 

ggplot(lnewdat, aes(x=month, y=Probability, color = Level))+ 
  geom_line() + facet_grid(cust_demographics_ai~cust_demographics_aii, labeller = "label_both")+ 
  ggtitle("Demographic Matrix") + scale_x_continuous(breaks=seq(1, 12, 1))

#Ordinal Logistic Regression 
#Account A
A<-polr(typeA_bal_cat~month+cust_demographics_ai+cust_demographics_aii+
          cust_outreach_ai+cust_outreach_aii+cust_outreach_aiii+cust_outreach_aiv+
          cust_outreach_av+cust_outreach_avi+cust_outreach_avii+
          channel_combination, data=bank_data, Hess=TRUE)

ctableA<-coef(summary(A))

pc<-pnorm(abs(ctableA[, "t value"]), lower.tail=FALSE *2)
(ctableA <- cbind(ctableA, "p value" = pc))

sort(exp(coef(A)), decreasing = TRUE)

A$coefficients<-exp(coef(A))

coefplot(A, zeroType = 0)

#Account B
B<-polr(typeB_bal_cat~+cust_demographics_ai+cust_demographics_aii+
          cust_outreach_ai+cust_outreach_aii+cust_outreach_aiii+cust_outreach_aiv+
          cust_outreach_avi+cust_outreach_avii+cust_outreach_aviii+
          channel_combination, data=bank_data, Hess=TRUE)

ctableB<-coef(summary(B))

pcB<-pnorm(abs(ctableB[, "t value"]), lower.tail=FALSE *2)
(ctableB <- cbind(ctableB, "p value" = pcB))

sort(exp(coef(B)), decreasing = TRUE)

B$coefficients<-exp(coef(B))
coefplot(B, zeroType = 0)

#Account C
C<-polr(typeC_bal_cat~month+cust_demographics_ai+cust_demographics_aii+
          cust_outreach_ai+cust_outreach_aii+
          cust_outreach_av+cust_outreach_avi+cust_outreach_aviii+
          channel_combination, data=bank_data, Hess=TRUE)

ctableC<-coef(summary(C))

pcC<-pnorm(abs(ctableC[, "t value"]), lower.tail=FALSE *2)
(ctableC <- cbind(ctableC, "p value" = pcC))

sort(format(exp(coef(C)), scientific = FALSE),decreasing = TRUE)

C$coefficients<-exp(coef(C))
coefplot(C, zeroType = 0)

#Account D
D<-polr(typeD_bal_cat~month+cust_demographics_ai+cust_demographics_aii+
          cust_outreach_ai+cust_outreach_aiii+
          cust_outreach_av+cust_outreach_avi+cust_outreach_avii+cust_outreach_aviii+
          channel_combination, data=bank_data, Hess=TRUE)

ctableD<-coef(summary(D))

pcD<-pnorm(abs(ctableD[, "t value"]), lower.tail=FALSE *2)
(ctableD <- cbind(ctableD, "p value" = pcD))

sort(format(exp(coef(D)), scientific = FALSE), decreasing = TRUE)

D$coefficients<-exp(coef(D))
coefplot(D, zeroType = 0)

#Account E
E<-polr(typeE_bal_cat~month+cust_demographics_ai+cust_demographics_aii+
          cust_outreach_ai + cust_outreach_aiii+ cust_outreach_aiv+
          cust_outreach_av+cust_outreach_avi+cust_outreach_avii+cust_outreach_aviii+
          channel_combination, data=bank_data, Hess=TRUE)

ctableE<-coef(summary(E))

pcE<-pnorm(abs(ctableE[, "t value"]), lower.tail=FALSE *2)
(ctableE <- cbind(ctableE, "p value" = pcE))

sort(format(exp(coef(E)), scientific = FALSE), decreasing = TRUE)

E$coefficients<-exp(coef(E))
coefplot(E, zeroType = 0)

#Account F
F_account<-glm(typeF_flag~month+cust_demographics_ai+cust_demographics_aii +
                 cust_outreach_ai+cust_outreach_aiv+cust_outreach_av+
                 cust_outreach_avi+cust_outreach_avii
               +channel_combination, data=bank_data, 
               family="binomial")

sort(exp(coef(F_account)), decreasing=TRUE)

F_account$coefficients<-exp(coef(F_account))
coefplot(F_account, zeroType = 0)

#Account G
G_account<-glm(typeG_flag~month+cust_demographics_aii+cust_outreach_ai+cust_outreach_aiv+
                 cust_outreach_avi+cust_outreach_avii+channel_combination, data=bank_data,family="binomial")

sort(exp(coef(G_account)), decreasing=TRUE)

G_account$coefficients<-exp(coef(G_account))
coefplot(G_account, zeroType = 0)


Prob_month1 <- subset(prediction, month == 1)
Prob_month12 <- subset(prediction, month == 12)

Prob_month1 <- Prob_month1[order(Prob_month1$cust_demographics_ai,Prob_month1$cust_demographics_aii),]
Prob_month12 <- Prob_month12[order(Prob_month12$cust_demographics_ai,Prob_month12$cust_demographics_aii),]

Prob_month1 <- Prob_month1[!duplicated(Prob_month1),]
Prob_month12 <- Prob_month12[!duplicated(Prob_month12),]

Prob_month1$decrease_slope <- (Prob_month12$`-1` - Prob_month1$`-1`) / 11
Prob_month1$increase_slope <- (Prob_month12$`1` - Prob_month1$`1`) / 11

ggplot(Prob_month1) + geom_point(aes(Prob_month1$increase_slope, Prob_month1$decrease_slope))

write.table(Prob_month1,file="output.csv",sep=",",row.names = FALSE)

# Use this output in tableau to create a heatmap


```

